An attempt to combine DE and DM data in the  Adenoid Cystic Carcinoma
========================================================

Alexander Favorov  
-----------------------------------------------

### `r format(Sys.Date(), "%d %b %Y")` 

`r opts_chunk$set(echo=FALSE, message=FALSE, warning=F, cache=F)`

First, we load tho sets of genes: those that are near (+-10000) the differetially methylated intervals (dm)` genes) and those that are diferentially expressed (de) genes.
their intersection is de.and.dm.

Each de gene is charaterised by the probability to be DE (PPDE). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

# gene lists for flanks 1000 around intevals with fdr<0.1

```{r}
de<-read.table('N_D_32s.ebseq.results.de_fdr0.05.sortRealFC.txt.gnames',header=TRUE)
dm<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.fdr.adjacent.genes.tsv',header=TRUE)
#dm.strict<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.bonf.adjacent.genes.tsv',header=TRUE)
de.and.dm<-intersect(de$GENE_NAME,dm$SYMBOL)
#de.and.dm.strict<-intersect(de$GENE_NAME,dm.strict$SYMBOL)

deindm<-de$GENE_NAME %in% de.and.dm
dminde<-dm$SYMBOL %in% de.and.dm

#deindmstrict<-de$GENE_NAME %in% de.and.dm.strict
```

`r length(dm$SYMBOL)` genes in dm;

`r length(de$GENE_NAME)` genes in de;

`r length(de.and.dm)` in de.and.dm

### DE vs DM

Comparing the probability of DE for DM genes and for all the non-DM DE genes.

```{r} 
boxplot(de$PPDE~deindm,main="Probability of DE for DM and for other DE genes", 
     ylab="PPDE", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PPDE~deindm)$p.value`)

The same for fold DE change (PostFC)


```{r} 
boxplot(de$PostFC~deindm,main="Fold of of DE for DM and for other DE genes", 
     ylab="PostFC", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PostFC~deindm)$p.value`)

### DM vs DE
Each dm gene is charaterised by the p-value (the closer to 0, the more oprobable is DM). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

```{r} 
boxplot(dm$p.value~dminde,main="Probability of DM for DE and for other DM genes", 
     ylab="p-value", xlab="In DE list")
```

Not significant, again (p-value=`r wilcox.test(dm$p.value~dminde)$p.value`)



### Direction of DE and DM 

Let's test whether the directions of de and dm are consistent.

```{r}

dm.direction<-sapply(de.and.dm,function(gene){dm$ishyper[which(dm$SYMBOL==gene)]})
de.direction<-sapply(de.and.dm,function(gene){de$PostFC[which(de$GENE_NAME==gene)]>1})

de.and.dm.direction<-table(de.direction,dm.direction)

print(de.and.dm.direction)
```
No correcpondence, looks like completely random Fisher table.

# DM gene lists for flanks 100000 around intevals with fdr<0.1

```{r}
#de<-read.table('N_D_32s.ebseq.results.de_fdr0.05.sortRealFC.txt.gnames',header=TRUE)
dm<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.fdr.adjacent.genes.100000.tsv',header=TRUE)

de.and.dm<-intersect(de$GENE_NAME,dm$SYMBOL)
#de.and.dm.strict<-intersect(de$GENE_NAME,dm.strict$SYMBOL)

deindm<-de$GENE_NAME %in% de.and.dm
dminde<-dm$SYMBOL %in% de.and.dm

#deindmstrict<-de$GENE_NAME %in% de.and.dm.strict
```

`r length(dm$SYMBOL)` genes in dm;

`r length(de$GENE_NAME)` genes in de;

`r length(de.and.dm)` in de.and.dm


### DE vs DM

```{r} 
boxplot(de$PPDE~deindm,main="Probability of DE for DM and for other DE genes", 
     ylab="PPDE", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PPDE~deindm)$p.value`)

The same for fold DE change (PostFC)


```{r} 
boxplot(de$PostFC~deindm,main="Fold of of DE for DM and for other DE genes", 
     ylab="PostFC", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PostFC~deindm)$p.value`)

### DM vs DE

Each dm gene is charaterised by the p-value (the closer to 0, the more oprobable is DM). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

```{r} 
boxplot(dm$p.value~dminde,main="Probability of DM for DE and for other DM genes", 
     ylab="p-value", xlab="In DE list")
```

Not significant, again (p-value=`r wilcox.test(dm$p.value~dminde)$p.value`)

### Direction of DE and DM 

Let's test whether the directions of de and dm are consistent.

```{r}
dm.direction<-sapply(de.and.dm,function(gene){dm$ishyper[which(dm$SYMBOL==gene)]})
de.direction<-sapply(de.and.dm,function(gene){de$PostFC[which(de$GENE_NAME==gene)]>1})

de.and.dm.direction<-table(de.direction,dm.direction)

print(de.and.dm.direction)
```

No correcpondence, looks like completely random Fisher table.

# DM gene lists for no flanks; intevals with fdr<0.1

```{r}
#de<-read.table('N_D_32s.ebseq.results.de_fdr0.05.sortRealFC.txt.gnames',header=TRUE)
dm<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.fdr.adjacent.genes.noflanks.tsv',header=TRUE)

de.and.dm<-intersect(de$GENE_NAME,dm$SYMBOL)
#de.and.dm.strict<-intersect(de$GENE_NAME,dm.strict$SYMBOL)

deindm<-de$GENE_NAME %in% de.and.dm
dminde<-dm$SYMBOL %in% de.and.dm

#deindmstrict<-de$GENE_NAME %in% de.and.dm.strict
```

`r length(dm$SYMBOL)` genes in dm;

`r length(de$GENE_NAME)` genes in de;

`r length(de.and.dm)` in de.and.dm


### DE vs DM

```{r} 
boxplot(de$PPDE~deindm,main="Probability of DE for DM and for other DE genes", 
     ylab="PPDE", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PPDE~deindm)$p.value`)

The same for fold DE change (PostFC)


```{r} 
boxplot(de$PostFC~deindm,main="Fold of of DE for DM and for other DE genes", 
     ylab="PostFC", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PostFC~deindm)$p.value`)

### DM vs DE
Each dm gene is charaterised by the p-value (the closer to 0, the more oprobable is DM). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

```{r} 
boxplot(dm$p.value~dminde,main="Probability of DM for DE and for other DM genes", 
     ylab="p-value", xlab="In DE list")
```

Not significant, again (p-value=`r wilcox.test(dm$p.value~dminde)$p.value`)

### Direction of DE and DM 

Let's test whether the directions of de and dm are consistent.

```{r}
dm.direction<-sapply(de.and.dm,function(gene){dm$ishyper[which(dm$SYMBOL==gene)]})
de.direction<-sapply(de.and.dm,function(gene){de$PostFC[which(de$GENE_NAME==gene)]>1})

de.and.dm.direction<-table(de.direction,dm.direction)

print(de.and.dm.direction)
```

No correspondence, looks like completely random Fisher table.

# DM gene lists for flanks 100000 around intevals with bonferroni-corrected DM intervals

```{r}
#de<-read.table('N_D_32s.ebseq.results.de_fdr0.05.sortRealFC.txt.gnames',header=TRUE)
dm<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.bonf.adjacent.genes.100000.tsv',header=TRUE)

de.and.dm<-intersect(de$GENE_NAME,dm$SYMBOL)
#de.and.dm.strict<-intersect(de$GENE_NAME,dm.strict$SYMBOL)

deindm<-de$GENE_NAME %in% de.and.dm
dminde<-dm$SYMBOL %in% de.and.dm

#deindmstrict<-de$GENE_NAME %in% de.and.dm.strict
```

`r length(dm$SYMBOL)` genes in dm;

`r length(de$GENE_NAME)` genes in de;

`r length(de.and.dm)` in de.and.dm


### DE vs DM

```{r} 
boxplot(de$PPDE~deindm,main="Probability of DE for DM and for other DE genes", 
     ylab="PPDE", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PPDE~deindm)$p.value`)

The same for fold DE change (PostFC)


```{r} 
boxplot(de$PostFC~deindm,main="Fold of of DE for DM and for other DE genes", 
     ylab="PostFC", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PostFC~deindm)$p.value`)

### DM vs DE
Each dm gene is charaterised by the p-value (the closer to 0, the more oprobable is DM). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

```{r} 
boxplot(dm$p.value~dminde,main="Probability of DM for DE and for other DM genes", 
     ylab="p-value", xlab="In DE list")
```

Not significant, again (p-value=`r wilcox.test(dm$p.value~dminde)$p.value`)

### Direction of DE and DM 

Let's test whether the directions of de and dm are consistent.

```{r}
dm.direction<-sapply(de.and.dm,function(gene){dm$ishyper[which(dm$SYMBOL==gene)]})
de.direction<-sapply(de.and.dm,function(gene){de$PostFC[which(de$GENE_NAME==gene)]>1})

de.and.dm.direction<-table(de.direction,dm.direction)

print(de.and.dm.direction)
```

No correspondence, looks like completely random Fisher table.

# DM gene lists for flanks 1000000 around intevals with bonferroni-corrected DM intervals

```{r}
#de<-read.table('N_D_32s.ebseq.results.de_fdr0.05.sortRealFC.txt.gnames',header=TRUE)
dm<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.bonf.adjacent.genes.1000000.tsv',header=TRUE)

de.and.dm<-intersect(de$GENE_NAME,dm$SYMBOL)
#de.and.dm.strict<-intersect(de$GENE_NAME,dm.strict$SYMBOL)

deindm<-de$GENE_NAME %in% de.and.dm
dminde<-dm$SYMBOL %in% de.and.dm

#deindmstrict<-de$GENE_NAME %in% de.and.dm.strict
```

`r length(dm$SYMBOL)` genes in dm;

`r length(de$GENE_NAME)` genes in de;

`r length(de.and.dm)` in de.and.dm


### DE vs DM

```{r} 
boxplot(de$PPDE~deindm,main="Probability of DE for DM and for other DE genes", 
     ylab="PPDE", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PPDE~deindm)$p.value`)

The same for fold DE change (PostFC)


```{r} 
boxplot(de$PostFC~deindm,main="Fold of of DE for DM and for other DE genes", 
     ylab="PostFC", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PostFC~deindm)$p.value`)

### DM vs DE

Each dm gene is charaterised by the p-value (the closer to 0, the more oprobable is DM). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

```{r} 
boxplot(dm$p.value~dminde,main="Probability of DM for DE and for other DM genes", 
     ylab="p-value", xlab="In DE list")
```

Not significant, again (p-value=`r wilcox.test(dm$p.value~dminde)$p.value`)

### Direction of DE and DM 

Let's test whether the directions of de and dm are consistent.

```{r}
dm.direction<-sapply(de.and.dm,function(gene){dm$ishyper[which(dm$SYMBOL==gene)]})
de.direction<-sapply(de.and.dm,function(gene){de$PostFC[which(de$GENE_NAME==gene)]>1})

de.and.dm.direction<-table(de.direction,dm.direction)

print(de.and.dm.direction)
```

No correspondence, looks like completely random Fisher table.

# gene lists for flanks 1000 around intevals with fdr<0.1 ; differectial expressio with PPDE>0.999

```{r}
de<-read.table('N_D_32s.ebseq.results.de_fdr0.05.sortRealFC.txt.gnames',header=TRUE)
de<-de[which(de$PPDE>0.999),]
dm<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.fdr.adjacent.genes.tsv',header=TRUE)
#dm.strict<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.bonf.adjacent.genes.tsv',header=TRUE)
de.and.dm<-intersect(de$GENE_NAME,dm$SYMBOL)
#de.and.dm.strict<-intersect(de$GENE_NAME,dm.strict$SYMBOL)

deindm<-de$GENE_NAME %in% de.and.dm
dminde<-dm$SYMBOL %in% de.and.dm

#deindmstrict<-de$GENE_NAME %in% de.and.dm.strict
```

`r length(dm$SYMBOL)` genes in dm;

`r length(de$GENE_NAME)` genes in de;

`r length(de.and.dm)` in de.and.dm

### DE vs DM

```{r} 
boxplot(de$PPDE~deindm,main="Probability of DE for DM and for other DE genes", 
     ylab="PPDE", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PPDE~deindm)$p.value`)

The same for fold DE change (PostFC)


```{r} 
boxplot(de$PostFC~deindm,main="Fold of of DE for DM and for other DE genes", 
     ylab="PostFC", xlab="In DM list")
```

The Wilcoxon test does not show significant difference (p-value=`r wilcox.test(de$PostFC~deindm)$p.value`)

### DM vs DE

Each dm gene is charaterised by the p-value (the closer to 0, the more oprobable is DM). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

```{r} 
boxplot(dm$p.value~dminde,main="Probability of DM for DE and for other DE genes", 
     ylab="p-value", xlab="In DE list")
```

Not significant, again (p-value=`r wilcox.test(dm$p.value~dminde)$p.value`)

### Direction of DE and DM 

Let's test whether the directions of de and dm are consistent.

```{r}

dm.direction<-sapply(de.and.dm,function(gene){dm$ishyper[which(dm$SYMBOL==gene)]})
de.direction<-sapply(de.and.dm,function(gene){de$PostFC[which(de$GENE_NAME==gene)]>1})

de.and.dm.direction<-table(de.direction,dm.direction)

print(de.and.dm.direction)
```

No correspondence, looks like completely random Fisher table.



