An attempt to combine DE and DM data in the 
========================================================

Alexander Favorov  
-----------------------------------------------

### `r format(Sys.Date(), "%d %b %Y")` 

`r opts_chunk$set(echo=FALSE, message=FALSE, warning=F, cache=F)`

```{r}
de<-read.table('N_D_32s.ebseq.results.de_fdr0.05.sortRealFC.txt.gnames',header=TRUE)
dm<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.fdr.adjacent.genes.tsv',header=TRUE)
#dm.strict<-read.table('../DiffMeth/genomewidenoodles/DM.M.noodles.bonf.adjacent.genes.tsv',header=TRUE)
de.and.dm<-intersect(de$GENE_NAME,dm$SYMBOL)
#de.and.dm.strict<-intersect(de$GENE_NAME,dm.strict$SYMBOL)

deindm<-de$GENE_NAME %in% de.and.dm
dminde<-dm$SYMBOL %in% de.and.dm

#deindmstrict<-de$GENE_NAME %in% de.and.dm.strict
```
First, we load tho sets of genes: those that are near (+-10000) the differetially methylated intervals (dm, `r length(dm$SYMBOL)` genes) and those that are diferentially expressed (de, `r length(de$GENE_NAME)` genes.
their intersection is de.and.dm and its length is `r length(de.and.dm)`.

Each de gene is charaterised by the probability to be DE (PPDE). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

### DE vs DM

```{r} 
boxplot(de$PPDE~deindm,main="Probability of DE for DM and for other DE genes", 
     ylab="PPDE", xlab="In DM list")
```

Let's compare the two sets by Wilcoxon test. The difference is not significant (p-value=`r wilcox.test(de$PPDE~deindm)$p.value`)

Each dm gene is charaterised by the p-value (the closer to 0, the more oprobable is DM). Lets's compare the value for the genes in the dm.and.de intersection and for the other genes.

### DM vs DE
```{r} 
boxplot(dm$p.value~dminde,main="Probability of DM for DE and for other DE genes", 
     ylab="p-value", xlab="In DE list")
```

Not significant, again (p-value=`r wilcox.test(dm$p.value~dminde)$p.value`)

### Direction of DE and DM 

Let's test whether the directions of de and dm are consistent.

```{r}
dm.direction<-sapply(de.and.dm,function(gene){dm$ishyper[which(dm$SYMBOL==gene)]})
de.direction<-sapply(de.and.dm,function(gene){de$PostFC[which(de$GENE_NAME==gene)]>1})

de.and.dm.direction<-table(de.direction,dm.direction)

print(de.and.dm.direction)
```

We see no consitency, alas!

